% Introduction

% Related Works

% Google App Engine
\newcommand{\ftGAEOne}[0]{\footnotemark[1]%
}
\newcommand{\ftGAEOneText}[0]{
\footnotetext[1]{Google App Engine. \emph{Why App Engine}, Retrieved May 14, 2012. https://developers.google.com/appengine/whyappengine}
}

\newcommand{\ftGAETwo}[0]{\footnotemark[2]%
}
\newcommand{\ftGAETwoText}[0]{
\footnotetext[2]{Google App Engine. \emph{What Is Google App Engine?}, Retrieved May 14, 2012. https://developers.google.com/appengine/docs/whatisgoogleappengine}
}

\newcommand{\ftGAEThree}[0]{\footnotemark[3]%
}
\newcommand{\ftGAEThreeText}[0]{
\footnotetext[3]{Google App Engine. \emph{Using the Master/Slave Datastore}, Retrieved May 14, 2012. https://developers.google.com/appengine/docs/java/datastore/usingmasterslave}
}

\newcommand{\ftGAEFour}[0]{\footnotemark[4]%
}
\newcommand{\ftGAEFourText}[0]{
\footnotetext[4]{Google App Engine. \emph{Datastore Overview}, Retrieved May 14, 2012. https://developers.google.com/appengine/docs/java/datastore/overview\#Datastore\_Writes\_and\_Data\_Visibility}
}

\newcommand{\ftGAEFive}[0]{\footnotemark[5]%
}
\newcommand{\ftGAEFiveText}[0]{
\footnotetext[5]{Google App Engine. \emph{Billing and Budgeting Resources}, Retrieved May 14, 2012. https://developers.google.com/appengine/docs/billing}
}

% Azure

\newcommand{\ftAone}[0]{\footnotemark[6]%
}
\newcommand{\ftAoneText}[0]{
\footnotetext[6]{Windows Azure. \emph{Home Page}, Retrieved May 14, 2012. http://www.windowsazure.com/en-us/}
}

\newcommand{\ftAimg}[0]{\footnotemark[7]%
}
\newcommand{\ftAimgText}[0]{
\footnotetext[7]{Temi Odurinde. \emph{Windows Azure -- Microsoft Clouds Computing}, Retrieved May 14, 2012. http://www.temi.co.uk/windows-azure-microsoft-clouds-computing/}
}

\newcommand{\ftAtwo}[0]{\footnotemark[8]%
}
\newcommand{\ftAtwoText}[0]{
\footnotetext[8]{Wikipedia. \emph{AppFabric}, Retrieved May 14, 2012. http://en.wikipedia.org/wiki/AppFabric}
}

\newcommand{\ftAthree}[0]{\footnotemark[9]%
}
\newcommand{\ftAthreeText}[0]{
\footnotetext[9]{GigaOM. \emph{Everything You Need to Know About Microsoft Azure}, Retrieved May 14, 2012. http://gigaom.com/2009/07/14/microsoft-azure/}
}

\newcommand{\ftAfour}[0]{\footnotemark[10]%
}
\newcommand{\ftAfourText}[0]{
\footnotetext[10]{Windows Azure. \emph{Windows Azure Storage}, Retrieved May 14, 2012. http://www.windowsazure.com/en-us/home/features/storage}
}

% Amazon EC2
\newcommand{\ftAmOne}[0]{\footnotemark[11]%
}
\newcommand{\ftAmOneText}[0]{
\footnotetext[11]{Wikipedia. \emph{Amazon Elastic Compute Cloud}, Retrieved May 14, 2012. http://en.wikipedia.org/wiki/Amazon\_Elastic\_Compute\_Cloud}
}

\newcommand{\ftAmTwo}[0]{\footnotemark[12]%
}
\newcommand{\ftAmTwoText}[0]{
\footnotetext[12]{Network World. \emph{Amazon uses nearly half a million servers to power EC2, researcher estimates}, Retrieved May 14, 2012. http://www.networkworld.com/news/2012/031612-amazon-ec2-257384.html}
}

\newcommand{\ftAmThree}[0]{\footnotemark[13]%
}
\newcommand{\ftAmThreeText}[0]{
\footnotetext[13]{Amazon Web Services. \emph{Amazon EC2 Instance Types}, Retrieved May 14, 2012. http://aws.amazon.com/ec2/instance-types/}
}

\newcommand{\ftAmFour}[0]{\footnotemark[14]%
}
\newcommand{\ftAmFourText}[0]{
\footnotetext[14]{Ars Technica. \emph{\$1,279-per-hour, 30,000-core cluster built on Amazon EC2 cloud}, Retrieved May 14, 2012. http://arstechnica.com/business/news/2011/09/30000-core-cluster-built-on-amazon-ec2-cloud.ars}
}

% Aneka

% System Comparisons
\newcommand{\ftSCspeed}[0]{\footnotemark[15]%
}
\newcommand{\ftSCspeedText}[0]{
\footnotetext[15]{CloudSleuth. \emph{Cloud Provider Page Delivery Time Ranking -- March}, Retrieved May 15, 2012. https://cloudsleuth.net/blog/cloud-provider-page-delivery-time-ranking-\%E2\%80\%93-march}
}

% Success Stories
\newcommand{\ftSgaeOne}[0]{\footnotemark[16]%
}
\newcommand{\ftSgaeOneText}[0]{
\footnotetext[16]{GigaPan. \emph{About GigaPan}, Retrieved May 14, 2012. http://www.gigapan.com/cms/about-us}
}

\newcommand{\ftSgaeTwo}[0]{\footnotemark[17]%
}
\newcommand{\ftSgaeTwoText}[0]{
\footnotetext[17]{Google Code Developer Conference. \emph{Interview with GigaPan Developers Rich Gibson, Gabrielle O'Donnel}, May 2009. http://www.google.com/events/io/2009/sandbox/gigapan.html}
}

\newcommand{\ftSgaeThree}[0]{\footnotemark[18]%
}
\newcommand{\ftSgaeThreeText}[0]{
\footnotetext[18]{Google App Engine. \emph{App Engine Developer Profiles}, Retrieved May 14, 2012. https://developers.google.com/appengine/casestudies\#gigapan}
}

\newcommand{\ftSAmOne}[0]{\footnotemark[19]%
}
\newcommand{\ftSAmOneText}[0]{
\footnotetext[19]{foursquare. \emph{About foursquare}, Retrieved May 14, 2012. https://foursquare.com/about/}
}

\newcommand{\ftSAmTwo}[0]{\footnotemark[20]%
}
\newcommand{\ftSAmTwoText}[0]{
\footnotetext[20]{Amazon Web Services. \emph{AWS Case Study: foursquare}, May 2009. http://aws.amazon.com/solutions/case-studies/foursquare/}
}

% Summary and Conclusions
